mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-06 Draft2.Rmd
denote commented

>>>>

## Abbreviations

\pkg{mathml} allows also for the use of abbreviations in formulas. Let us consider here the t-statistic for independent samples with equal variance assumed. 
The procedure consists of three steps. The first one is to define the hooks to nicely print the variables. Second, we write the t-statistic specifying in the formula how to calculate the pooled variance with the function  `denote(abbr, expr, info)`.  Finally, since \pkg{mathml} also allows computation, we can directly compute the value of the t statistic with `eval()`.

hook(quote(x_1), quote(mean(x["1"])))
hook(quote(x_2), quote(mean(x["2"])))
hook(quote(n_1), quote(n["1"]))
hook(quote(n_2), quote(n["2"]))
hook(quote(s_1), quote(s["1"]))
hook(quote(s_2), quote(s["2"]))
hook(quote(s_p), quote(s["pool"]))

t <- quote(dfrac(x_1 - x_2, sqrt(denote(s_p^2L, frac((n_1 - 1L)*s_1^2L + (n_2 - 1L)*s_2^2L, n_1+n_2-2L), "the pooled variance.") * (dfrac(1L, n_1)+dfrac(1L,n_2)))))

mathout(t)

# An example

x_1 = 20.5
x_2 = 35.7
n_1 = 150
n_2 = 160
s_1 = 3.4
s_2 = 4.2

eval(t)
```
